\vspace{24pt} Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application

### 2018-08-24 paper/paper.tex
title2
update motivation

\title{
  % \includegraphics[width=0.2\textwidth]{hpi_logo_2017}\\
  \vspace{24pt}
  % In-Memory Trajectory Analysis on Taxi Data
  Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Application
}
\subtitle{
  Seminar Trends and Concepts 3\\
  Summer Semester 2018
}

@@

>>>>

\title{
  % \includegraphics[width=0.2\textwidth]{hpi_logo_2017}\\
  \vspace{24pt}
  % In-Memory Trajectory Analysis on Taxi Data
  Comparison of Different Data Layouts for Columnar In-Memory Databases on the Basis of an Example Application
}
\subtitle{
  Seminar Trends and Concepts 3\\
  Summer Semester 2018
}

@@

Storing trajectory data in traditional relational databases is not always the best idea. Requests might take a long time when working on big data sets. It is also difficult to achieve good compression rates. There exist some systems which are purely designed to work with such trajectories. Those systems are performing much better than the traditional databases.

In our project we would like to investiage how a columnar in-memory database can handle trajectory data. Thereby, we can make use of the in-memory architecture and of the columnar storage benefits. We developed an example application which covers a lot of real world requests to a large trajectory data set. This application builds a good basis to benchmark different data layouts and optimizations.
